### 2016-01-26 Manuscript/BiologyLetters/Supplementary/ESM_2.tex
Updated email

\bigskip
\noindent {\normalsize \sc Thomas Guillerme$^1$$^,$$^*$ and Natalie Cooper$^1$$^,$$^2$}\\
\noindent {\small \it 
$^1$School of Natural Sciences, Trinity College Dublin, Dublin 2, Ireland.\\
$^2$Department of Life Sciences, Natural History Museum, Cromwell Road, London, SW7 5BD, UK.}\\
\medskip
\noindent{*\bf Corresponding author.} \textit{guillert@tcd.ie}\\  
\vspace{1in}

@@

\section{Supplementary results - 1}
The following section contains supplementary results to the main body: the available data structure using the NTI and the PD metric; the proportion of available data and the data structure for all the matrices (including the matrices with less than 100 characters).

\input{Results_1c/Results_1cTable_results}

>>>>

\bigskip
\noindent {\normalsize \sc Thomas Guillerme$^1$$^,$$^*$ and Natalie Cooper$^1$$^,$$^2$}\\
\noindent {\small \it 
$^1$School of Natural Sciences, Trinity College Dublin, Dublin 2, Ireland.\\
$^2$Department of Life Sciences, Natural History Museum, Cromwell Road, London, SW7 5BD, UK.}\\
\medskip
\noindent{*\bf Corresponding author.} \textit{t.guillerme@imperial.ac.uk}\\  
\vspace{1in}

@@

\section{Supplementary results - 2}
The following section contains supplementary results to the main body: the phylogenetic representation of the data availability per order (excluding Primates and Carnivora, present in the main body).

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supp_figure_AFROSORICIDA.pdf}
\caption{Distribution of available morphological data across Afrosoricida. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Afrosoricida}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supp_figure_CHIROPTERA.pdf}
\caption{Distribution of available morphological data across Chiroptera. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Chiroptera}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supp_figure_CINGULATA.pdf}
\caption{Distribution of available morphological data across Cingulata. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Cingulata}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supp_figure_DASYUROMORPHIA.pdf}
\caption{Distribution of available morphological data across Dasyuromorphia. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Dasyuromorphia}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supp_figure_DIDELPHIMORPHIA.pdf}
\caption{Distribution of available morphological data across Didelphimorphia. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Didelphimorphia}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supp_figure_DIPROTODONTIA.pdf}
\caption{Distribution of available morphological data across Diprotodontia. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Diprotodontia}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supp_figure_ERINACEOMORPHA.pdf}
\caption{Distribution of available morphological data across Erinaceomorpha. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Erinaceomorpha}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supp_figure_PILOSA.pdf}
\caption{Distribution of available morphological data across Pilosa. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Pilosa}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supp_figure_CETARTIODACTYLA.pdf}
\caption{Distribution of available morphological data across Cetartiodactyla. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Primates}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supp_figure_RODENTIA.pdf}
\caption{Distribution of available morphological data across Rodentia. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Rodentia}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supp_figure_SCANDENTIA.pdf}
\caption{Distribution of available morphological data across Scandentia. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Scandentia}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supp_figure_SORICOMORPHA.pdf}
\caption{Distribution of available morphological data across Soricomorpha. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Soricomorpha}
\end{figure}
